Learning \strips\ Action Models from State Observations

### 2018-01-10 doc/ijcai-18/observations-learning.tex

\begin{table}
		\begin{center}
\begin{scriptsize}                
				\begin{tabular}{l|l|l|l|l|l|l||l|l|}
					& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
					& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
					\hline
					Blocks & 0.86 & 0.67 & 0.71 & 0.56 & 0.86 & 0.67 & 0.81 & 0.63 \\
					Driverlog & 0.40 & 0.14 & 0.36 & 0.57 & 0.50 & 0.29 & 0.42 & 0.33 \\
					Ferry & 0.50 & 0.29 & 0.33 & 0.50 & 0.50 & 0.50 & 0.44 & 0.43 \\
					Floortile & 0.67 & 0.36 & 0.67 & 0.36 & 1.0 & 0.36 & 0.78 & 0.36 \\
					Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
					Gripper & 1.0 & 0.67 & 0.75 & 0.75 & 0.75 & 0.75 & 0.83 & 0.72 \\
					Hanoi & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.83 \\
					Hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Parking & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Satellite & 0.40 & 0.14 & 0.43 & 0.60 & 0.67 & 0.50 & 0.50 & 0.41 \\
					Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Transport & 0.75 & 0.30 & 0.67 & 0.80 & 1.0 & 0.60 & 0.81 & 0.57 \\
					Zenotravel & 1.0 & 0.29 & 0.50 & 0.43 & 1.0 & 0.43 & 0.83 & 0.38 \\
					\hline
					\bf  & 0.73 & 0.36 & 0.60 & 0.62 & 0.81 & 0.57 & 0.71 & 0.52 \\
				\end{tabular}
	\end{scriptsize}
		\end{center}
 \caption{\small Precision and recall values obtained when learning from labels without computing the $f_{P\&R}$ mapping.}
\label{fig:labelsnomap}

\begin{center}
\begin{scriptsize}                
				\begin{tabular}{l|l|l|l|l|l|l||l|l|}
					& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
					& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
					\hline
					Blocks & 0.86 & 0.67 & 0.71 & 0.56 & 0.86 & 0.67 & 0.81 & 0.63 \\
					Driverlog & 0.40 & 0.14 & 0.36 & 0.57 & 0.50 & 0.29 & 0.42 & 0.33 \\
					Ferry & 0.50 & 0.29 & 0.33 & 0.50 & 0.50 & 0.50 & 0.44 & 0.43 \\
					Floortile & 0.67 & 0.36 & 0.67 & 0.36 & 1.0 & 0.36 & 0.78 & 0.36 \\
					Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
					Gripper & 1.0 & 0.67 & 0.75 & 0.75 & 0.75 & 0.75 & 0.83 & 0.72 \\
					Hanoi & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.83 \\
					Hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Parking & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Satellite & 0.40 & 0.14 & 0.43 & 0.60 & 0.67 & 0.50 & 0.50 & 0.41 \\
					Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
					Transport & 0.75 & 0.30 & 0.67 & 0.80 & 1.0 & 0.60 & 0.81 & 0.57 \\
					Zenotravel & 1.0 & 0.29 & 0.50 & 0.43 & 1.0 & 0.43 & 0.83 & 0.38 \\
					\hline
					\bf  & 0.73 & 0.36 & 0.60 & 0.62 & 0.81 & 0.57 & 0.71 & 0.52 \\
				\end{tabular}
	\end{scriptsize}
		\end{center}
 \caption{\small Precision and recall values obtained when learning from labels but computing the $f_{P\&R}$ mapping.}
\label{fig:labels}                
\end{table}

@@

\begin{table}
	\begin{scriptsize}
		\begin{center}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				Blocks & 0.75 & 0.67 & 0.71 & 0.56 & 0.71 & 0.56 & 0.73 & 0.59 \\
				Driverlog & 0.67 & 0.29 & 0.38 & 0.71 & 0.60 & 0.43 & 0.55 & 0.48 \\
				Ferry & 0.75 & 0.43 & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 & 0.64 \\
				Floortile & - & - & - & - & - & - & - & - \\ % Ctrl C
				Grid & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Gripper & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 \\
				Hanoi & 0.50 & 0.25 & 0.0 & 0.0 & 0.50 & 0.50 & 0.33 & 0.25 \\
				Hiking & - & - & - & - & - & - & - & - \\ % Ctrl C
				Parking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Satellite & 0.40 & 0.14 & 0.43 & 0.60 & 0.67 & 0.50 & 0.50 & 0.41 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Transport & - & - & - & - & - & - & - & - \\ % Ctrl C
				Zenotravel & 1.0 & 0.29 & 0.50 & 0.43 & 1.0 & 0.43 & 0.83 & 0.38 \\
				\hline
				\bf  & 0.72 & 0.39 & 0.54 & 0.58 & 0.72 & 0.60 & 0.67 & 0.52 \\
			\end{tabular}
		\end{center}
	\end{scriptsize}
 \caption{\small Precision and recall values obtained when learning from labels + invariants.}
\label{fig:invariants}
\end{table}

@@

\begin{table}
	\begin{footnotesize}
		\begin{center}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				Blocks & 0.71 & 0.56 & 0.60 & 0.67 & 0.71 & 0.56 & 0.68 & 0.59 \\
				Ferry & 0.75 & 0.43 & 0.50 & 0.75 & 0.75 & 0.75 & 0.67 & 0.64 \\
				Gripper & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 \\
				Hanoi & 0.50 & 0.25 & 0.0 & 0.0 & 0.50 & 0.50 & 0.33 & 0.25 \\
				\hline
				\bf  & 0.74 & 0.48 & 0.53 & 0.61 & 0.74 & 0.70 & 0.67 & 0.57 \\
			\end{tabular}
		\end{center}
	\end{footnotesize}
  \caption{\small Precision and recall values obtained when learning from observations.}
\label{fig:observations}       
\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{scriptsize}                
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.57 & 0.44 & 0.63 & 0.56 & 0.57 & 0.44 & 0.59 & 0.48 \\
				driverlog & 0.2 & 0.07 & 0.18 & 0.29 & 0.2 & 0.14 & 0.19 & 0.17 \\
				ferry & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				floor-tile & 0.5 & 0.14 & 0.75 & 0.55 & 0.6 & 0.27 & 0.62 & 0.32 \\
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 0.25 & 0.17 & 0.25 & 0.25 & 0.25 & 0.25 & 0.25 & 0.22 \\
				hanoi & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				n-puzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				parking & 0.6 & 0.21 & 0.14 & 0.11 & 0.4 & 0.22 & 0.38 & 0.18 \\
				satellite & 0.25 & 0.07 & 0.33 & 0.4 & 0.67 & 0.5 & 0.42 & 0.32 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 0.33 & 0.1 & 0.33 & 0.4 & 0.0 & 0.0 & 0.22 & 0.17 \\
				zeno-travel & 0.25 & 0.07 & 0.17 & 0.14 & 0.0 & 0.0 & 0.14 & 0.07 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained when learning from labels without computing the $f_{P\&R}$ mapping.}
	\label{fig:labelsnomap}

	\begin{center}
		\begin{scriptsize}                
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.71 & 0.56 & 0.75 & 0.67 & 0.71 & 0.56 & 0.73 & 0.59 \\
				driverlog & 0.6 & 0.21 & 0.27 & 0.43 & 0.6 & 0.43 & 0.49 & 0.36 \\
				ferry & 0.5 & 0.29 & 0.75 & 0.75 & 0.5 & 0.5 & 0.58 & 0.51 \\
				floor-tile & 0.5 & 0.14 & 0.75 & 0.55 & 0.6 & 0.27 & 0.62 & 0.32 \\
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 \\
				hanoi & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				n-puzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				parking & 0.6 & 0.21 & 0.14 & 0.11 & 0.4 & 0.22 & 0.38 & 0.18 \\
				satellite & 0.25 & 0.07 & 0.33 & 0.4 & 0.67 & 0.5 & 0.42 & 0.32 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 1.0 & 0.3 & 0.67 & 0.8 & 0.67 & 0.4 & 0.78 & 0.5 \\
				zeno-travel & 0.5 & 0.14 & 0.5 & 0.43 & 0.33 & 0.14 & 0.44 & 0.24 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained when learning from labels but computing the $f_{P\&R}$ mapping.}
	\label{fig:labels}                
\end{table}

@@

\begin{table}[hbt!]
	\begin{scriptsize}
		\begin{center}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.63 & 0.56 & 0.71 & 0.56 & 0.71 & 0.56 & 0.68 & 0.56 \\
				Driverlog & - & - & - & - & - & - & - & - \\ % Time out 1000s
				ferry & 0.75 & 0.43 & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 & 0.64 \\
				Floortile & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 0.8 & 0.67 & 0.75 & 0.75 & 1.0 & 1.0 & 0.85 & 0.81 \\                                                                                                                                                                       
				Hanoi & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Npuzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Parking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Satellite & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Transport & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Zenotravel & - & - & - & - & - & - & - & - \\ % Time out 1000s
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{center}
	\end{scriptsize}
	\caption{\small Precision and recall values obtained when learning from labels + invariants.}
	\label{fig:invariants}
\end{table}

@@

\begin{table}
	\begin{footnotesize}
		\begin{center}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.78 & 0.78 & 0.78 & 0.78 & 0.78 & 0.78 & 0.78 & 0.78 \\
				driverlog & 0.75 & 0.64 & 0.86 & 0.86 & 0.86 & 0.86 & 0.82 & 0.79 \\
				ferry & 0.86 & 0.86 & 0.75 & 0.75 & 0.75 & 0.75 & 0.79 & 0.79 \\
				Floortile & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 1.0 & 0.67 & 0.8 & 1.0 & 1.0 & 1.0 & 0.93 & 0.89 \\
				hanoi & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\                                                                                                                                                                                     
				Hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Npuzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				parking & 0.8 & 0.57 & 1.0 & 0.78 & 1.0 & 0.78 & 0.93 & 0.71 \\
				Satellite & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				Transport & - & - & - & - & - & - & - & - \\ % Time out 1000s
				zeno-travel & 1.0 & 0.43 & 1.0 & 0.71 & 1.0 & 0.71 & 1.0 & 0.62 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{center}
	\end{footnotesize}
	\caption{\small Precision and recall values obtained when learning from observations.}
	\label{fig:observations}       
\end{table}
